---
title: "Indian Startup Scenario"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```
## Importing the libraries
### Here we import all the libraries we will need for the data analysis

```{r}
library(tidyverse)
library(ggplot2)
library(formattable)
library(gt)
library(dplyr)
library(stringr)
library(DT)
```

## Data reading and cleaning

First we will read the data 
```{r}
options(scipen = 999)
data <- read.csv("C:/Users/Prashant/Downloads/Indian Startup.csv")

```

Lets have a look at the data

I will list out column names

```{r}
colnames(data)

```

As we can see that our data consists of information about the brand,founding year, city of origin, investors etc..

Now we will clean and filter the data as per our requirements

Here i have filtered the database to reflect the data from 2010 to 2020 as this study will be focussed on these 10 years.

```{r}
data <- data %>%
  filter(Founded > '2010' & Founded <= '2020')
```

Here we will format the columns for proper datatypes and removing incorrect data from the dataset

```{r}
data$Amount = str_sub(data$Amount,2,20)
data$Amount = gsub(",","",data$Amount,fixed = TRUE)
data$Amount[data$Amount == 'Undisclosed'] <- 0
data$Amount <- as.numeric(data$Amount)
data <- remove_missing(data)
data$Founded <- as.character((data$Founded),format = "%Y")
```


### We are about to dive into an analysis of the data about the startups in India and funding that they have received over the years.

### Number of startups founded from 2010 to 2020

```{r}
ggplot(data %>%
         filter(Headquarters %in% head(data %>%
                                       count(Headquarters,sort = 10),n = 10)$Headquarters[c(1:5)])) +
         geom_bar(mapping = aes(x = Founded,fill = Headquarters),position = 'dodge')
```

### Top funded 10 sectors

The overall top funded sectors of the market
```{r}
datatable(data %>%
  select(Sector,Amount)%>%
  group_by(Sector)%>%
  summarise(tot_am = sum(Amount))%>%
  arrange(desc(tot_am))) %>% formatCurrency('tot_am',"$")
```

### How did different sectors got funded in the last 5 years?

```{r}
ggplot(data %>%
         filter(Founded == 2016) %>%
         select(Sector,Amount,Founded) %>%
         group_by(Sector,Founded) %>%
         summarize(tot_amount=sum(Amount))%>%
         arrange(desc(tot_amount))%>%
         head(n = 5)) +
  geom_col(mapping = aes(x = Sector,y = tot_amount,fill = Sector))+
  labs(title = 'Top 5 sectors in 2016',x = 'Sector',y = 'Total Amount Funded')+
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```
```{r echo = FALSE}
ggplot(data %>%
         filter(Founded == 2017) %>%
         select(Sector,Amount,Founded) %>%
         group_by(Sector,Founded) %>%
         summarize(tot_amount=sum(Amount))%>%
         arrange(desc(tot_amount))%>%
         head(n = 5)) +
  geom_col(mapping = aes(x = Sector,y = tot_amount,fill = Sector))+
  labs(title = 'Top 5 sectors in 2017',x = 'Sector',y = 'Total Amount Funded')+
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```
```{r echo = FALSE}
ggplot(data %>%
         filter(Founded == 2018) %>%
         select(Sector,Amount,Founded) %>%
         group_by(Sector,Founded) %>%
         summarize(tot_amount=sum(Amount))%>%
         arrange(desc(tot_amount))%>%
         head(n = 5)) +
  geom_col(mapping = aes(x = Sector,y = tot_amount,fill = Sector))+
  labs(title = 'Top 5 sectors in 2018',x = 'Sector',y = 'Total Amount Funded')+
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```
```{r echo = FALSE}
ggplot(data %>%
         filter(Founded == 2019) %>%
         select(Sector,Amount,Founded) %>%
         group_by(Sector,Founded) %>%
         summarize(tot_amount=sum(Amount))%>%
         arrange(desc(tot_amount))%>%
         head(n = 5)) +
  geom_col(mapping = aes(x = Sector,y = tot_amount,fill = Sector))+
  labs(title = 'Top 5 sectors in 2019',x = 'Sector',y = 'Total Amount Funded')+
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```
```{r echo = FALSE}
ggplot(data %>%
         filter(Founded == 2020) %>%
         select(Sector,Amount,Founded) %>%
         group_by(Sector,Founded) %>%
         summarize(tot_amount=sum(Amount))%>%
         arrange(desc(tot_amount))%>%
         head(n = 5)) +
  geom_col(mapping = aes(x = Sector,y = tot_amount,fill = Sector))+
  labs(title = 'Top 5 sectors in 2020',x = 'Sector',y = 'Total Amount Funded')+
  scale_x_discrete(guide = guide_axis(n.dodge=2))
```

### Top 10 cities with startups

This is table of top 10 cities with highest number of startups over the period of 10 years

```{r}
data %>%
  count(Headquarters,sort = TRUE) %>%
  head(n = 10) %>%
  gt(rowname_col = 'Headquarters') %>%
  tab_header(
    title = md('Top 10 cities with startups')
  ) %>%
  cols_label(n = 'Number of Startups') %>%
  cols_align(align = 'center')%>%
  cols_width(n ~ px(100))
```


